---
title: 'faoebx5 overview'
date: '`r Sys.Date()`'
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
    vignette: >
      %\VignetteIndexEntry{valr-overview}
      %\VignetteEngine{knitr::rmarkdown}
      %\VignetteEncoding{UTF-8}
---

```{r knitr_opts, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center"
)

options(width = 95)
```

The first time you use the `faoebx5` package you must set your EBX credentials. In this step your credetials will be sotred in the safe way, for this we have used the [`keyring`](https://CRAN.R-project.org/package=keyring) R package. If you would not store your credentials, you should use the function `RemoveEBXCredentials()`.

Once you have typed your password twice after run `SetEBXCredentials()` function, you do not need to rerun this function, because your credential will be kept.

```{r eval=TRUE, include=TRUE, message=FALSE}
library('faoebx5')
SetEBXCredentials()
```

# Code Lists  

TODO

## GetEBXCodeLists()

This function aimed to get the list of code list available in the EBX5.

```{r eval=TRUE, include=TRUE}
ebx_cl <- GetEBXCodeLists()
ebx_cl[1:15, ]
```

## ReadEBXCodeList()

TODO

```{r eval=TRUE, include=TRUE}
cl_isscfc <- ReadEBXCodeList(cl_name = 'ISSCFC')
head(cl_isscfc)
```

## InsertEBXCodeList()

TODO

```{r eval=FALSE, include=TRUE}
InsertEBXCodeList(data     = cl_isscfc_new,
                  cl_name  = 'FAO_Level1',
                  folder   = 'Commodity',
                  branch   = 'Fishery',
                  instance = 'Fishery')
```

## UpdateEBXCodeList()

TODO

```{r eval=FALSE, include=TRUE}
UpdateEBXCodeList(cl_name = 'EBXCodelist',
                  folder = 'Metadata',
                  data = cl_update)
```
