---
title: 'faoebx5 overview'
date: '`r Sys.Date()`'
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
    vignette: >
      %\VignetteIndexEntry{valr-overview}
      %\VignetteEngine{knitr::rmarkdown}
      %\VignetteEncoding{UTF-8}
---

```{r knitr_opts, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center"
)

options(width = 95)
```

The first time you use the `faoebx5` package you must set your EBX credentials. In this step your credetials will be sotred in the safe way, for this we have used the [`keyring`](https://CRAN.R-project.org/package=keyring) R package. If you would not store your credentials, you should use the function `RemoveEBXCredentials()`.

Once you have typed your password twice after run `SetEBXCredentials()` function, you do not need to rerun this function, because your credential will be kept.

```{r eval=TRUE, include=TRUE, message=FALSE}
library('faoebx5')
library('dplyr')
SetEBXCredentials()
```

## GetEBXCodeLists()

This function aimed to get the list of code list available in the EBX5. It has two arguments: `branch` and `instance` that default values are set as <span class="badge badge-danger">"Fishery"</span>.

```{r eval=TRUE, include=TRUE}
ebx_cl <- GetEBXCodeLists()
head(ebx_cl)
```

## ReadEBXCodeList()

This function aimed to read code list data from EBX5 to R. As we can see, 

```{r eval=TRUE, include=TRUE}
cl_fao_level1 <- ReadEBXCodeList(cl_name = 'FAO_Level1 ')
cl_fao_level1 %>% tbl_df()
```

<hr>

<div class="alert alert-dismissible alert-warning">
  <button type="button" class="close" data-dismiss="alert">&times;</button>
  <h4 class="alert-heading">Warning!</h4>
  <p class="mb-0">Please, be aware that the next two functions can modify the original data. Anyway, we should have permition to do changes in the original data.</p>
</div>

<hr>

## InsertEBXCodeList()

TODO

```{r eval=FALSE, include=TRUE}
InsertEBXCodeList(data     = cl_isscfc_new,
                  cl_name  = 'FAO_Level1',
                  folder   = 'Commodity',
                  branch   = 'Fishery',
                  instance = 'Fishery')
```

## UpdateEBXCodeList()

TODO

```{r eval=FALSE, include=TRUE}
UpdateEBXCodeList(cl_name = 'EBXCodelist',
                  folder = 'Metadata',
                  data = cl_update)
```
